Requirements and Current State of Knowledge Representation Systems for Service Robotics

### 2012-05-10 krs-survey.tex
Shortcomings:Added assessment of performances

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[grow=right, sibling distance=5mm, level distance = 3.5cm]
    \node {\bf F. Knowledge instantiation}
            child {node {{\bf F.4} Alignement with Standards}}
            child {node {{\bf F.3} Self-Knowledge}}
            child {node {{\bf F.2} Metrics}}
            child {node {{\bf F.1} Design Strategy}};
 \end{tikzpicture}
\end{center}
\end{scriptsize}

\subsubsection{Design Strategy}

Ontology engineering has grown into a research field of its own\fxwarning{Give
some idea about it? wikipedia?}.

Two main approaches are common in the cognitive robotic community:
\emph{top-down} design and \emph{bottom-up}.

Several strategies ... Designing, implementing and feeding an ontological model of the beliefs of the robot

\begin{itemize}
    \item Dynamic, run-time instantiation
    \item Static, a priori knowledge
    \item Fetch from external resources (TBox and/or ABox)
\end{itemize}

\subsubsection{Metrics}

Qualitative and quantitative metrics give an oversight of the size and
expressive complexity of ontologies.

Table~\ref{table|upper_onto_metrics} gives such metrics for four major
upper-ontologies commonly used in the semantic Web community.

\fxwarning{Add metrics for SUMO, OpenCyc, ResearchCyc}

\begin{table}
\begin{center}

\begin{tabular}{llllll}
\toprule
{\bf Project} & {\bf Expressiveness} & {\bf Axioms} & {\bf Classes} & {\bf Properties} & {\bf Instances} \\
\midrule
OpenCyc \\
ResearchCyc \\
SUMO \\
DBPedia \\
\bottomrule

\end{tabular}
\end{center}
\caption{Selection of metrics for the major upper-ontologies.}
\label{table|upper_onto_metrics}
\end{table}

@@

\subsubsection{Alignment with Standard Upper-ontologies}

>>>>

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[grow=right, sibling distance=5mm, level distance = 3.5cm]
    \node {\bf F. Knowledge instantiation}
            child {node {{\bf F.2} Alignement with Standards}}
            child {node {{\bf F.1} Self-Knowledge}}
 \end{tikzpicture}
\end{center}
\end{scriptsize}

How much knowledge is available? Which content? How big is the knowledge base?

\begin{itemize}
	\item  Which underlying knowledge (\emph{common-sense}, \emph{upper knowledge}\ldots{})
	\begin{itemize}
		\item  top-down approach?
	\end{itemize}

@@

\subsubsection{Alignment with Standard Upper-Ontologies}
